# JS in Shiny

## Add JS to Shiny

How to add JavaScript to `{shiny}`?

### With `{golem}`

```{r eval = FALSE}
golem::add_js_file()
```

> Simple JS file

```{r eval = FALSE}
golem::add_js_handler()
```

> Shiny Handlers

### Link in your app

#### With `tags$script`

+ If you have a file:

```{r eval = FALSE}
tags$script(src = "www/script.js")
```

+ Write the JS code straight in the app:

```{r eval = FALSE}
tags$script(
  HTML("var x = ['plop', 'pouet'];
  x.forEach(x => alert(x))
  ")
)
```

#### With `htmlDependency()`

+ Create an `htmlDependency` object:

```{r}
dep_binding <- function() {
  htmlDependency(
    "dep","0.1.0",
    src = system.file("app/www", package = "expl"),
    stylesheet = c(
      "css/uikit.css",
      "css/custom.css"
    ),
    script = c(
      "input-fleche.js",
      "input-nav.js",
      "input-progress.js",
      "input-rangeSlider.js", 
      "input-select.js",
      "input-onoff.js", 
      "input-sqonOff.js", 
      "input-radioButton.js",
      "input-checkbox.js",
      "input-increment.js",
      "panel.js"
    ), 
    meta = list(
      lang="fr"
    ),
    head = HTML(
      '<meta http-equiv="X-UA-Compatible" content=="IE=edge"/>
        <meta name="viewport" content="width=device-width, initial-scale=1">
        <link href="https://fonts.googleapis.com/css?family=Raleway:400,600,700|Roboto+Slab:300,400,700" rel="stylesheet"> '
    )
  )
}

```

Then in `R/app_ui.R`

```{r}
golem_add_external_resources <- function(){
  
  #...
  dr_binding()
}
```

## The JavaScript Shiny Object 

In the browser, there is a `Shiny` JavaScript object.

### Set the value of an input from JavaScript

+ From your browser, you can set the value of a Shiny input:

```{js eval = FALSE}
Shiny.setInputValue(id, value, options)
```

> With `{priority : 'event'}`, the value is sent even if the value hasn't changed (not the default behavior)

```{js eval = FALSE}
Shiny.setInputValue("pouet", 12, {priority : 'event'})
```

> `pouet` will appear as `input$pouet`

```{r eval = FALSE}
observeEvent( input$pouet , {

})
```


## Shiny JS Handlers

+ Pass data from R to JS (from server to browser)

```{js}
Shiny.addCustomMessageHandler('alert', function(arg) {
  alert(arg.val);
  alert(arg.size);
});
```

+ Send with `session$sendCustomMessage()`

+ To pass multiple value, pass a list, then access with `.name`

```{r eval = FALSE}
session$sendCustomMessage("alert", list(
  val = 2, 
  size = 11
))
```

