# Examples

```{r include = FALSE}
knitr::opts_chunk$set(eval = FALSE, comment = "#")
```

## ColinFay/tidytuesday201942

+ On load, this allows to hide all the contents (with the class `row`) and to show only the first. 
+ The first `nav-link` is set to active.

```{js}
$(function(){
  $( ".row" ).hide();
  $( ".row" ).first().show();
  $( ".nav-link" ).first().addClass("active");
  var h = parseInt($('nav').outerHeight()) + 30;
  $(".row").css("padding-top", h + "px");
})
```

## Toast

+ Using Boostrap 4 toast 

```
<div id = "globalerror" class="toast global-toast" data-delay = "5000">
  <div class="toast-body">
    <span>&#10060;</span> <span> Application error</span>
  </div>
</div>
```

```{js}
Shiny.addCustomMessageHandler('errortoast', function(id) {
    $("#globalerror").toast("show")
});
  
Shiny.addCustomMessageHandler('successtoast', function(id) {
    $("#globalsuccess").toast("show")
});
```

```{r eval = FALSE}
error_toast <- function(){
  golem::invoke_js("errortoast", TRUE)
  NULL
}
```

## Prompt sthg 

+ This function will open a prompt, ask something to the user, and send it back to R on the `input$idout`

```{js}
function prompt_name(idout){
  var nom = prompt("Enter a name for your blabla");
  if (nom === null) {
    return;
  }
  Shiny.setInputValue(idout, nom,  {priority: 'event'});
}
```

```{r eval = FALSE}
tags$button(
  class = "btn btn-default action-button",
  "Save blabla", 
  onclick = sprintf(
    "prompt_name('%s')",
    save_id
  )
)
```

## Fixed nav

+ This makes a navbar follow the scroll of the page

```{js}
document.addEventListener('scroll', function (event) {
  var yoff = window.pageYOffset;
  var h = parseInt($('nav').outerHeight());
  $(".fixed-nav").css("top", (h - yoff) + "px");
}, true);
```

## Get the width of an element from R

+ Ask for the width of a div:

```{js}
Shiny.addCustomMessageHandler("getwidth", function(what) {
  var w = document.getElementById(what).clientWidth;
  Shiny.setInputValue('divheight', w);
});
```

+ Then use this width to render the plot:

```{r eval = FALSE}
session$sendCustomMessage("getwidth", ns("biggy"))
# ... 
plotOutput(
  ns("gg_waffer"), 
  width = as.character(round(input$biggy * 0.7))
)
```

## Get number of click

```{js}
var add_val_and_send = function(e, id, nom){
  com = "";
  $(e).data('value', $(e).data('value') + 1 );
  Shiny.setInputValue(id, {com : nom, val : $(e).data('value')}, {priority : "event"});
}
```

```{r eval = FALSE}
li_custom_context(
  ns("ligne"), 
  "La ligne", 
  `data-value` = 10,
  sprintf(
    "add_val_and_send(this, '%s', '%s')",
    ns("ligne"), nom
  )
)
```

## Add a message to a menu element 

+ When the user clicks on the tab, they'll get asked if they confirm that they want to restart the app

```{js}
$(function(){
  var x = $('a[href="#shiny-tab-demarrage"]');
  x.attr("href", "javascript:void(0)");
  x.attr("onclick", "var x = confirm( 'Do you want to restart the app?' ); if(x){ window.location = window.location };");
})

```

## Hide and sho specific elements

```{js}
$( document ).ready(function() {
  Shiny.addCustomMessageHandler('show_year', function(arg) {
    $("#single > div.col-sm-3.well > div:nth-child(5)").hide()
    $("#single > div.col-sm-3.well > div:nth-child(7)").hide()
    $("#single > div.col-sm-3.well > div:nth-child(3)").show()
  })
  Shiny.addCustomMessageHandler('show_artist', function(arg) {
    $("#single > div.col-sm-3.well > div:nth-child(3)").hide()
    $("#single > div.col-sm-3.well > div:nth-child(7)").hide()
    $("#single > div.col-sm-3.well > div:nth-child(5)").show()
  })
  Shiny.addCustomMessageHandler('show_label', function(arg) {
    $("#single > div.col-sm-3.well > div:nth-child(3)").hide()
    $("#single > div.col-sm-3.well > div:nth-child(5)").hide()
    $("#single > div.col-sm-3.well > div:nth-child(7)").show()
  })
  
});
```

## Success alert 

```{r}
tags$div(
  class="alert alert-success", 
  id = "alert-success",
  tags$a(
    class="close", 
    "X"
  ), 
  "Success!"
)
```


```{js}
$( document ).ready(function() {
  Shiny.addCustomMessageHandler('success', function(content) {
    $("#alert-success").show();
  });
});
```

## Adapt size of div to screen 

```{js}
// https://stackoverflow.com/questions/1038727/how-to-get-browser-width-using-javascript-code
function getWidth() {
  if (self.innerWidth) {
    return self.innerWidth;
  }

  if (document.documentElement && document.documentElement.clientWidth) {
    return document.documentElement.clientWidth;
  }

  if (document.body) {
    return document.body.clientWidth;
  }
}

function makelarge(){
  var arr_width = $(".arrow").innerWidth() * 2 + 64 * 2;
  $(".tabrow").not(".inner").css("width", (getWidth() - arr_width) + "px");
}

window.onresize = makelarge
```

