--- 
title: "JS 4 Shiny - Field Notes"
author: "Colin Fay"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "Oui."
---

# Field Notes on JavaScript for Shiny Users {-}

```{r include = FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = "#")
```

## About this bookdown

This Bookdown is the content of an informal JavaScript training given inside ThinkR. 
It's in no way supposed to be a complete JavaScript course nor even a complete book. 
Most of the content is composed of pieces of code + comments, without complete sentences. 
Please read it with this in mind.

Also, this Bookdown is `{shiny}`-centric so focuse on things that can be used when building Shiny-apps. 

## Installing `{bubble}` {-}

+ R package to interact with NodeJS  

__Note: you'll need to have NodeJS installed on your machine__

```{r}
if (!requireNamespace("bubble")){
  remotes::install_github("ColinFay/bubble")
}
```

+ Set the `{knitr}` engine for Rmds

```{r}
bubble::set_node_engine()
```

+ Access a NodeJS REPL 

```{r eval = FALSE}
node_repl()
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```


